### 2020-12-12 paper/localpsf.tex
more intro editing

We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
\begin{equation}
\label{eq:wi_optimization_problem_intro}
\begin{aligned}
\min_{w_i} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$ with pure Neumann boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness [cite Jacobsen], the functions $w_i$ are the flattest functions, in a least-squares sense, that interpolate the points $x_i$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation [cite Escande etc], is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.

>>>>

We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
\begin{equation}
\label{eq:wi_optimization_problem_intro}
\begin{aligned}
\min_{w_i} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$ with pure Neumann boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness [CITE JACOBSEN], the functions $w_i$ are the flattest functions, in a least-squares sense, that interpolate the points $x_i$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation [cite Escande etc], is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.
